\vspace{-2.25cm} Multimodal Abnormity-Aware Model\\for Ocular Disease Diagnosis

### 2024-09-01 Paper/Paper.tex
revise fig and table captions

	\vspace{-0.2cm}
	\hrule
	\vspace{-0.1cm}
	\section*{Abstract}
	\hrule
	\vspace{0.4cm}
	We devise a novel model, the Multimodal Abnormity-Aware Model (MAAM), for assisting ocular disease diagnosis. The MAAM enables input of 2 kinds of ophthalmological images, namely optical coherence tomography (OCT) and color fundus images, and simulates the decision-making process by deducing the disease from abnormities. The model is composed of 2 submodels, the Abnormity Models and the Diagnosis Model, where the Abnormity Models identify 11 OCT abnormities and 8 fundus abnormities, and the Diagnosis Model identifies 12 diseases by integrating features from the former model. In MAAM, we introduce the fusion mechanics, the concept of codominant abnormities and diseases, and the Abnormity-to-Disease Criteria.  The model breaks the black box of complex neural network and expose more interpretable information for the reference of ophthalmologists. And it gets the overall accuracy of 89\% and thus the feasibility is verified.
	\vspace{0.4cm}
	\hrule
	\vspace{1cm}

@@

	\begin{figure}[htbp]
	\centering
	\includegraphics[width=\linewidth]{Figs/model_overview.pdf}
	\caption{Model Overview}
	\vspace{0.3cm}
	\label{fig:3_parts}
	\end{figure}

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=\linewidth]{Figs/OCT_Abnormities.pdf}
		\caption{OCT Abnormities \autocite{Duker_Waheed_Goldman_2022}}
		\vspace{0.3cm}
		\label{fig:OCT_abnormities}
	\end{figure}

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=\linewidth]{Figs/fundus_Abnormities.pdf}
		\caption{Fundus Abnormities \autocite{Wolf_Kirchhof_Reim_2006}}
		\vspace{0.3cm}
		\label{fig:fundus_abnormities}
	\end{figure}

@@

	\begin{figure}[htbp]
	\centering
	\includegraphics[width=\linewidth]{Figs/fusion.pdf}
	\caption{Fusion}
	\vspace{0.3cm}
	\label{fig:fusion}
	\end{figure}

@@

	\vspace{-0.5cm}
	\begin{minipage}[t]{0.4\linewidth}
		{
			\fontsize{9}{12}\selectfont
			{
				\begin{longtable}{cccccc}
					\caption{OCT abnormities}
					\label{tb:OCT_source}\\
					\toprule
					\multirow{2}{*}{Abnormity}&\multicolumn{4}{c}{Source}&\multirow{2}{*}{Total}\\
					&1&2&3&4&\\
					\midrule
					CNV    &2984&-  &- &- &2984\\
					CSC    &-   &102&32&- &134 \\
					DME    &2500&-  &- &- &2500\\
					Drusen &2500&-  &- &- &2500\\
					ERM    &-   &-  &- &16&16  \\
					IF     &1097&-  &- &- &1097\\
					MH     &-   &99 &31&- &130 \\
					Mactel &-   &-  &29&- &29  \\
					Healthy&5000&-  &- &- &5000\\
					RP     &-   &102&31&- &133 \\
					ST     &-   &-  &23&- &23  \\
					SF     &1083&-  &- &- &1083\\
					\bottomrule
				\end{longtable}

@@

				\vspace{0.5cm}
			}
		}
	\end{minipage}
	\begin{minipage}[t]{0.6\linewidth}
		{
			\fontsize{9}{12}\selectfont
			{
				\begin{longtable}{cccccccc}
					\caption{Fundus abnormities}
					\label{tb:Fundus_source}\\
					\toprule
					\multirow{2}{*}{Abnormity}&\multicolumn{6}{c}{Source}&\multirow{2}{*}{Total}\\
					&1&2&3&4&5&6&\\
					\midrule
					CWP    &-  &- &- &33 &205&- &238\\
					Drusen &-  &- &- &50 &-  &- &50 \\     
					HE     &20 &- &- &75 &284&- &379\\ 
					HM     &13 &66&- &105&278&- &462\\     
					MH     &-  &- &- &-  &-  &34&34 \\        
					MA     &55 &- &- &1  &219&- &275\\
					Healthy&100&37&15&-  &-  &- &152\\      
					RP     &-  &22&- &-  &-  &44&66 \\         
					VA     &-  &64&- &14 &-  &- &78 \\

@@

	{
		\fontsize{9}{12}\selectfont
		{
			\begin{longtable}{ccccc}
				\caption{OCT images CycleGAN adoption rates}
				\label{tb:cycleGAN_number}\\
				\toprule
				Abnormity&Original&Generated&Adopted&Adoption Rate\\
				\midrule
				CSC   &134&3000&1730&58.667\% \\
				ERM   &19 &3000&1931&64.367\% \\
				MH    &130&3000&1811&60.367\% \\
				Mactel&29 &3000&1900&63.333\% \\
				RP    &133&3000&1923&63.100\% \\
				ST    &23 &3000&2572&86.067\% \\
				\bottomrule
			\end{longtable}
		}
	}

@@

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=\linewidth]{Figs/abnormity_OCT_loss_and_acc.pdf}
		\includegraphics[width=\linewidth]{Figs/abnormity_Fundus_loss_and_acc.pdf}
		\caption{Abnormity training}
		\label{fig:A_train}
	\end{figure}

	{
	\fontsize{9}{12}\selectfont
	{
		\begin{table}
			\centering
			\caption{Overall accuracies}
			\label{tb:A_accuracies}
			\begin{tabular}{ccccc}
				\toprule
				Model&ResNet152&ResNet50&ResNet18&VGG16\\
				\midrule
				OCT Model   &91.906\%&\textbf{92.183\%}&91.011\%&89.744\% \\
				Fundus Model&\textbf{89.111\%}&88.926\%&86.605\%&79.185\% \\
				\bottomrule
			\end{tabular}
		\end{table}
	}
	}

	\begin{table}[htbp]
		\centering
		\fontsize{9}{12}\selectfont{
		\caption{OCT Test}
		\label{tb:OCT_test}
		\pgfplotstabletypeset[
		multicolumn names,
		col sep=comma,
		columns = {Abnormity, Precision, Sensitivity, Specificity, FOne, AUC},
		columns/Abnormity/.style={string type, column name=Abnormities},
		columns/Precision/.style={string type, column name=Precision},
		columns/Sensitivity/.style={string type, column name=Sensitivity},
		columns/Specificity/.style={string type, column name=Specificity},
		columns/FOne/.style={string type, column name={F1 Score}},
		columns/AUC/.style={string type, column name=AUC},
		every head row/.style={before row=\toprule, after row=\midrule},
		every last row/.style={ after row=\bottomrule}
		]{Tables/abnormity_o_test.csv}}
	\end{table}
	\begin{table}[H]
		\centering
		\fontsize{9}{12}\selectfont{
		\caption{Fundus Test}
		\label{tb:Fundus_test}
		\pgfplotstabletypeset[
		multicolumn names,
		col sep=comma,
		columns = {Abnormity, Precision, Sensitivity, Specificity, FOne, AUC},
		columns/Abnormity/.style={string type, column name=Abnormities},
		columns/Precision/.style={string type, column name=Precision},
		columns/Sensitivity/.style={string type, column name=Sensitivity},
		columns/Specificity/.style={string type, column name=Specificity},
		columns/FOne/.style={string type, column name={F1 Score}},
		columns/AUC/.style={string type, column name=AUC},
		every head row/.style={before row=\toprule, after row=\midrule},
		every last row/.style={after row=\bottomrule}
		]{Tables/abnormity_f_test.csv}}
	\end{table}

@@

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=\linewidth]{Figs/abnormity_ROC.pdf}
		\caption{A ROC}
		\vspace{0.3cm}
		\label{fig:A_ROC}
	\end{figure}

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=\linewidth]{Figs/abnormity_confusion_matrix.pdf}
		\caption{A Conf Mat}
		\vspace{0.3cm}
		\label{fig:A_conf_mat}
	\end{figure}

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=\linewidth]{Figs/abnormity_tSNE.pdf}
		\caption{A ROC}
		\vspace{0.3cm}
		\label{fig:A_tSNE}
	\end{figure}

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=\linewidth]{Figs/abnormity_gradCAM.pdf}
		\caption{GradCAM}
		\vspace{0.3cm}
		\label{fig:gradCAM}
	\end{figure}

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=0.8\linewidth]{Figs/abnormity_gradCAM_multiple_abnormities.pdf}
		\caption{GradCAM with multiple abnormities}
		\vspace{0.3cm}
		\label{fig:gradCAM_multi_abnormity}
	\end{figure}

@@

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=\linewidth]{Figs/diagnosis1_confusion_matrix.pdf}
		\caption{D1 Conf Mat}
		\vspace{0.3cm}
		\label{fig:D1_conf_mat}
	\end{figure}

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=\linewidth]{Figs/diagnosis1_acc_barchart.pdf}
		\caption{D1 Acc Bar}
		\vspace{0.3cm}
		\label{fig:D1_acc_bar}
	\end{figure}

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=\linewidth]{Figs/diagnosis2_ROC.pdf}
		\caption{D2 ROC}
		\vspace{0.3cm}
		\label{fig:D2_ROC}
	\end{figure}

	\begin{figure}[H]
		\centering
		\includegraphics[width=0.7\linewidth]{Figs/diagnosis2_confusion_matrix.pdf}
		\vspace{-0.8cm}
		\caption{D2 Conf Mat}
		\label{fig:D2_conf_mat}
	\end{figure}

	\begin{figure}[H]
		\centering
		\includegraphics[width=0.65\linewidth]{Figs/diagnosis2_tSNE.pdf}
		\vspace{-0.3cm}
		\caption{D2 tSNE}
		\label{fig:D2_tSNE}
	\end{figure}

		\begin{table}[H]
		\centering
		\fontsize{9}{12}\selectfont{
			\caption{Diagnosis Test}
			\label{tb:diagnosis_test}
			\pgfplotstabletypeset[
			multicolumn names,
			col sep=comma,
			columns = {Abnormity, Precision, Sensitivity, Specificity, FOne, AUC},
			columns/Abnormity/.style={string type, column name=Abnormities},
			columns/Precision/.style={string type, column name=Precision},
			columns/Sensitivity/.style={string type, column name=Sensitivity},
			columns/Specificity/.style={string type, column name=Specificity},
			columns/FOne/.style={string type, column name={F1 Score}},
			columns/AUC/.style={string type, column name=AUC},
			every head row/.style={before row=\toprule, after row=\midrule},
			every last row/.style={ after row=\bottomrule}
			]{Tables/diagnosis2.csv}}
	\end{table}

>>>>

	\vspace{-0.2cm}
	\hrule
	\vspace{-0.1cm}
	\section*{Abstract}
	\hrule
	\vspace{0.4cm}
	We devise a novel model, the Multimodal Abnormity-Aware Model (MAAM), for assisting ocular disease diagnosis. The MAAM enables input of 2 kinds of ophthalmological images, namely optical coherence tomography (OCT) and color fundus images, and simulates the decision-making process by deducing the disease from abnormities. The model is composed of 2 submodels, the Abnormity Models and the Diagnosis Model, where the Abnormity Models identify 11 OCT abnormities and 8 fundus abnormities, and the Diagnosis Model identifies 12 diseases by integrating features from the former model. In MAAM, we introduce the fusion mechanism, the concept of codominant abnormities and diseases, and the Abnormity-to-Disease Criteria.  The model breaks the black box of complex neural network and expose more interpretable information for the reference of ophthalmologists. And it gets the overall accuracy of 89\% and thus the feasibility is verified.
	\vspace{0.4cm}
	\hrule
	\vspace{1cm}

@@

	\begin{figure}[htbp]
	\centering
	\includegraphics[width=\linewidth]{Figs/model_overview.pdf}
	\caption{Model overview}
	\vspace{0.3cm}
	\label{fig:3_parts}
	\end{figure}

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=\linewidth]{Figs/OCT_Abnormities.pdf}
		\caption{OCT abnormities \autocite{Duker_Waheed_Goldman_2022}}
		\vspace{0.3cm}
		\label{fig:OCT_abnormities}
	\end{figure}

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=\linewidth]{Figs/fundus_Abnormities.pdf}
		\caption{Fundus abnormities \autocite{Wolf_Kirchhof_Reim_2006}}
		\vspace{0.3cm}
		\label{fig:fundus_abnormities}
	\end{figure}

@@

	\begin{figure}[htbp]
	\centering
	\includegraphics[width=\linewidth]{Figs/fusion.pdf}
	\caption{Fusion mechanism}
	\vspace{0.3cm}
	\label{fig:fusion}
	\end{figure}

@@

	\vspace{-0.5cm}
	\begin{minipage}[t]{0.4\linewidth}
		{
			\fontsize{9}{12}\selectfont
			{
				\begin{longtable}{cccccc}
					\caption{Data sources of OCT abnormities}
					\label{tb:OCT_source}\\
					\toprule
					\multirow{2}{*}{Abnormity}&\multicolumn{4}{c}{Source}&\multirow{2}{*}{Total}\\
					&1&2&3&4&\\
					\midrule
					CNV    &2984&-  &- &- &2984\\
					CSC    &-   &102&32&- &134 \\
					DME    &2500&-  &- &- &2500\\
					Drusen &2500&-  &- &- &2500\\
					ERM    &-   &-  &- &16&16  \\
					IF     &1097&-  &- &- &1097\\
					MH     &-   &99 &31&- &130 \\
					Mactel &-   &-  &29&- &29  \\
					Healthy&5000&-  &- &- &5000\\
					RP     &-   &102&31&- &133 \\
					ST     &-   &-  &23&- &23  \\
					SF     &1083&-  &- &- &1083\\
					\bottomrule
				\end{longtable}

@@

				\vspace{0.5cm}
			}
		}
	\end{minipage}
	\begin{minipage}[t]{0.6\linewidth}
		{
			\fontsize{9}{12}\selectfont
			{
				\begin{longtable}{cccccccc}
					\caption{Data sources of fundus abnormities}
					\label{tb:Fundus_source}\\
					\toprule
					\multirow{2}{*}{Abnormity}&\multicolumn{6}{c}{Source}&\multirow{2}{*}{Total}\\
					&1&2&3&4&5&6&\\
					\midrule
					CWP    &-  &- &- &33 &205&- &238\\
					Drusen &-  &- &- &50 &-  &- &50 \\     
					HE     &20 &- &- &75 &284&- &379\\ 
					HM     &13 &66&- &105&278&- &462\\     
					MH     &-  &- &- &-  &-  &34&34 \\        
					MA     &55 &- &- &1  &219&- &275\\
					Healthy&100&37&15&-  &-  &- &152\\      
					RP     &-  &22&- &-  &-  &44&66 \\         
					VA     &-  &64&- &14 &-  &- &78 \\

@@

	{
		\fontsize{9}{12}\selectfont
		{
			\begin{longtable}{ccccc}
				\caption{Adoption rates of Cycle-GAN-generated OCT images}
				\label{tb:cycleGAN_number}\\
				\toprule
				Abnormity&Original&Generated&Adopted&Adoption Rate\\
				\midrule
				CSC   &134&3000&1730&58.667\% \\
				ERM   &19 &3000&1931&64.367\% \\
				MH    &130&3000&1811&60.367\% \\
				Mactel&29 &3000&1900&63.333\% \\
				RP    &133&3000&1923&63.100\% \\
				ST    &23 &3000&2572&86.067\% \\
				\bottomrule
			\end{longtable}
		}
	}

@@

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=\linewidth]{Figs/abnormity_OCT_loss_and_acc.pdf}
		\includegraphics[width=\linewidth]{Figs/abnormity_Fundus_loss_and_acc.pdf}
		\caption{Abnormity Models training }
		\label{fig:A_train}
	\end{figure}

	{
	\fontsize{9}{12}\selectfont
	{
		\begin{table}
			\centering
			\caption{Overall accuracies using different CNNs}
			\label{tb:A_accuracies}
			\begin{tabular}{ccccc}
				\toprule
				Model&ResNet152&ResNet50&ResNet18&VGG16\\
				\midrule
				OCT Model   &91.906\%&\textbf{92.183\%}&91.011\%&89.744\% \\
				Fundus Model&\textbf{89.111\%}&88.926\%&86.605\%&79.185\% \\
				\bottomrule
			\end{tabular}
		\end{table}
	}
	}

	\begin{table}[htbp]
		\centering
		\fontsize{9}{12}\selectfont{
		\caption{Test results of the OCT Model}
		\label{tb:OCT_test}
		\pgfplotstabletypeset[
		multicolumn names,
		col sep=comma,
		columns = {Abnormity, Precision, Sensitivity, Specificity, FOne, AUC},
		columns/Abnormity/.style={string type, column name=Abnormities},
		columns/Precision/.style={string type, column name=Precision},
		columns/Sensitivity/.style={string type, column name=Sensitivity},
		columns/Specificity/.style={string type, column name=Specificity},
		columns/FOne/.style={string type, column name={F1 Score}},
		columns/AUC/.style={string type, column name=AUC},
		every head row/.style={before row=\toprule, after row=\midrule},
		every last row/.style={ after row=\bottomrule}
		]{Tables/abnormity_o_test.csv}}
	\end{table}
	\begin{table}[H]
		\centering
		\fontsize{9}{12}\selectfont{
		\caption{Test results of the Fundus Model}
		\label{tb:Fundus_test}
		\pgfplotstabletypeset[
		multicolumn names,
		col sep=comma,
		columns = {Abnormity, Precision, Sensitivity, Specificity, FOne, AUC},
		columns/Abnormity/.style={string type, column name=Abnormities},
		columns/Precision/.style={string type, column name=Precision},
		columns/Sensitivity/.style={string type, column name=Sensitivity},
		columns/Specificity/.style={string type, column name=Specificity},
		columns/FOne/.style={string type, column name={F1 Score}},
		columns/AUC/.style={string type, column name=AUC},
		every head row/.style={before row=\toprule, after row=\midrule},
		every last row/.style={after row=\bottomrule}
		]{Tables/abnormity_f_test.csv}}
	\end{table}

@@

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=\linewidth]{Figs/abnormity_ROC.pdf}
		\caption{ROCs of the Abnormity Models}
		\vspace{0.3cm}
		\label{fig:A_ROC}
	\end{figure}

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=\linewidth]{Figs/abnormity_confusion_matrix.pdf}
		\caption{Confusion matrices of the Abnormity Models}
		\vspace{0.3cm}
		\label{fig:A_conf_mat}
	\end{figure}

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=\linewidth]{Figs/abnormity_tSNE.pdf}
		\caption{t-SNE graph of the Abnormity Models}
		\vspace{0.3cm}
		\label{fig:A_tSNE}
	\end{figure}

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=\linewidth]{Figs/abnormity_gradCAM.pdf}
		\caption{Grad-CAM highlighting of abnormities}
		\vspace{0.3cm}
		\label{fig:gradCAM}
	\end{figure}

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=0.8\linewidth]{Figs/abnormity_gradCAM_multiple_abnormities.pdf}
		\caption{GradCAM highlighting of multiple abnormities}
		\vspace{0.3cm}
		\label{fig:gradCAM_multi_abnormity}
	\end{figure}

@@

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=\linewidth]{Figs/diagnosis1_confusion_matrix.pdf}
		\caption{Confusion matrices of Stage D1}
		\vspace{0.3cm}
		\label{fig:D1_conf_mat}
	\end{figure}

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=\linewidth]{Figs/diagnosis1_acc_barchart.pdf}
		\caption{Accuracies of the Diagnosis Model (*: accuracy in terms of the disease with highest probability; **: accuracy in terms of codominant diseases)}
		\vspace{0.3cm}
		\label{fig:D1_acc_bar}
	\end{figure}

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=\linewidth]{Figs/diagnosis2_ROC.pdf}
		\caption{ROCs of Stage D2}
		\vspace{0.3cm}
		\label{fig:D2_ROC}
	\end{figure}

	\begin{figure}[H]
		\centering
		\includegraphics[width=0.7\linewidth]{Figs/diagnosis2_confusion_matrix.pdf}
		\vspace{-0.8cm}
		\caption{Confusion matrix of Stage D2}
		\label{fig:D2_conf_mat}
	\end{figure}

	\begin{figure}[H]
		\centering
		\includegraphics[width=0.65\linewidth]{Figs/diagnosis2_tSNE.pdf}
		\vspace{-0.3cm}
		\caption{t-SNE graph of Stage D2}
		\label{fig:D2_tSNE}
	\end{figure}

		\begin{table}[H]
		\centering
		\fontsize{9}{12}\selectfont{
			\caption{Test results of Stage D2}
			\label{tb:diagnosis_test}
			\pgfplotstabletypeset[
			multicolumn names,
			col sep=comma,
			columns = {Abnormity, Precision, Sensitivity, Specificity, FOne, AUC},
			columns/Abnormity/.style={string type, column name=Abnormities},
			columns/Precision/.style={string type, column name=Precision},
			columns/Sensitivity/.style={string type, column name=Sensitivity},
			columns/Specificity/.style={string type, column name=Specificity},
			columns/FOne/.style={string type, column name={F1 Score}},
			columns/AUC/.style={string type, column name=AUC},
			every head row/.style={before row=\toprule, after row=\midrule},
			every last row/.style={ after row=\bottomrule}
			]{Tables/diagnosis2.csv}}
	\end{table}
